Assignment 2

### 2019-06-29 ex2/report/report.tex
Updated report

@@

 \begin{table*}
 \caption{Logistic regression coefficients as surrogate model for deep learning (left side) and random forests (right side).} \label{tab:logreg_coeff}
\begin{tabular}{l r r} \toprule 
\multirow{2}{*}{Feature} & \multicolumn{2}{c}{Training on} \\
  & predicted labels & real labels \\ \midrule
    \#srcTCPflag:ack &  -28.431 $\pm$ 1.129 &  -19.570 $\pm$ 6.735 \\
             srcPkts &  -26.661 $\pm$ 0.994 &  -18.099 $\pm$ 6.500 \\
     mean\_dstPktIAT &   16.232 $\pm$ 1.091 &   18.778 $\pm$ 1.396 \\
     mean\_srcPktIAT &  -12.140 $\pm$ 1.144 &  -15.672 $\pm$ 1.289 \\
            dstBytes &  -11.305 $\pm$ 0.361 &   -1.878 $\pm$ 6.300 \\
             dstPkts &   -9.750 $\pm$ 0.158 &   -3.987 $\pm$ 1.972 \\
      min\_dstPktIAT &   -9.216 $\pm$ 1.157 &  -12.533 $\pm$ 1.477 \\
            srcBytes &   -8.994 $\pm$ 4.744 &   -5.373 $\pm$ 3.870 \\
    \#dstTCPflag:ack &   -8.292 $\pm$ 0.227 &   -2.616 $\pm$ 1.952 \\
       stdev\_dstTTL &   -6.934 $\pm$ 0.231 &   -0.241 $\pm$ 0.014 \\
%   min\_srcPktLength &   -4.519 $\pm$ 0.314 &   -2.891 $\pm$ 0.180 \\
%         min\_srcTTL &   -4.192 $\pm$ 0.646 &   -3.619 $\pm$ 0.432 \\
% stdev\_srcPktLength &   -4.068 $\pm$ 0.342 &   -2.231 $\pm$ 0.439 \\
% stdev\_dstPktLength &    3.466 $\pm$ 0.085 &    3.289 $\pm$ 0.253 \\
%    stdev\_srcPktIAT &    3.102 $\pm$ 0.407 &    4.743 $\pm$ 0.475 \\
%            protocol &   -3.043 $\pm$ 0.028 &   -2.157 $\pm$ 0.012 \\
%    stdev\_dstPktIAT &   -2.842 $\pm$ 0.375 &   -4.545 $\pm$ 0.503 \\
%  mean\_srcPktLength &    2.339 $\pm$ 0.435 &    1.777 $\pm$ 0.261 \\
%         max\_srcTTL &    2.153 $\pm$ 0.820 &    2.448 $\pm$ 0.249 \\
%    \#srcTCPflag:fin &   -2.117 $\pm$ 0.066 &   -1.876 $\pm$ 0.045 \\
%      max\_srcPktIAT &   -2.044 $\pm$ 0.271 &   -3.821 $\pm$ 0.415 \\
%    \#srcTCPflag:syn &    1.738 $\pm$ 0.010 &    1.521 $\pm$ 0.005 \\
%   max\_dstPktLength &   -1.256 $\pm$ 0.066 &   -1.187 $\pm$ 0.137 \\
%  mean\_dstPktLength &    1.200 $\pm$ 0.019 &    1.008 $\pm$ 0.085 \\
%        mean\_srcTTL &   -0.858 $\pm$ 0.533 &   -0.709 $\pm$ 0.417 \\
%    \#dstTCPflag:syn &   -0.778 $\pm$ 0.021 &   -1.020 $\pm$ 0.011 \\
%         max\_dstTTL &   -0.695 $\pm$ 0.028 &   -1.369 $\pm$ 0.052 \\
%             dstPort &   -0.679 $\pm$ 0.002 &   -0.633 $\pm$ 0.004 \\
%      min\_srcPktIAT &   -0.111 $\pm$ 0.977 &   -0.762 $\pm$ 2.837 \\
%   max\_srcPktLength &    0.498 $\pm$ 0.048 &   -0.475 $\pm$ 0.432 \\
%         min\_dstTTL &    0.468 $\pm$ 0.023 &   -0.197 $\pm$ 0.109 \\
%            duration &   -0.415 $\pm$ 0.007 &   -0.386 $\pm$ 0.042 \\
%             srcPort &    0.345 $\pm$ 0.007 &    0.350 $\pm$ 0.005 \\
%   min\_dstPktLength &    0.268 $\pm$ 0.009 &    0.142 $\pm$ 0.021 \\
%      max\_dstPktIAT &    0.225 $\pm$ 0.267 &    2.307 $\pm$ 0.432 \\
%    \#dstTCPflag:fin &   -0.103 $\pm$ 0.024 &   -0.112 $\pm$ 0.017 \\
%        mean\_dstTTL &   -0.069 $\pm$ 0.016 &    1.436 $\pm$ 0.116 \\
%    \#srcTCPflag:cwr &    0.059 $\pm$ 0.034 &    0.052 $\pm$ 0.013 \\
%       stdev\_srcTTL &   -0.051 $\pm$ 0.025 &   -0.058 $\pm$ 0.012 \\
%    \#dstTCPflag:cwr &    0.016 $\pm$ 0.001 &   -0.014 $\pm$ 0.005 \\

@@

>>>>

\begin{table}
\caption{Detection performance results.} \label{tab:performance_results}
\begin{tabular}{l r r} \toprule
& Random Forest & Deep Learning \\ \midrule
Accuracy	&	0.9974 $\pm$ 0.0001	&	0.9970 $\pm$ 0.0002	\\
Precision	&	0.9965 $\pm$ 0.0001	&	0.9979 $\pm$ 0.0001	\\
Recall	&	0.9931 $\pm$ 0.0002	&	0.9903 $\pm$ 0.0007	\\
F1	&	0.9948 $\pm$ 0.0001	&	0.9941 $\pm$ 0.0004	\\
Youden	&	0.9920 $\pm$ 0.0002	&	0.9896 $\pm$ 0.0007	\\
\bottomrule
\end{tabular}
\end{table}

@@

 \begin{table*}
 \caption{Logistic regression coefficients as surrogate model for deep learning (left side) and random forests (right side) with backdoor.} \label{tab:logreg_coeff_bd}
\begin{tabular}{l r r} \toprule 
\multirow{2}{*}{Feature} & \multicolumn{2}{c}{Training on} \\
  & predicted labels & real labels \\ \midrule
    \#srcTCPflag:ack &  -28.431 $\pm$ 1.129 &  -19.570 $\pm$ 6.735 \\
             srcPkts &  -26.661 $\pm$ 0.994 &  -18.099 $\pm$ 6.500 \\
     mean\_dstPktIAT &   16.232 $\pm$ 1.091 &   18.778 $\pm$ 1.396 \\
     mean\_srcPktIAT &  -12.140 $\pm$ 1.144 &  -15.672 $\pm$ 1.289 \\
            dstBytes &  -11.305 $\pm$ 0.361 &   -1.878 $\pm$ 6.300 \\
             dstPkts &   -9.750 $\pm$ 0.158 &   -3.987 $\pm$ 1.972 \\
      min\_dstPktIAT &   -9.216 $\pm$ 1.157 &  -12.533 $\pm$ 1.477 \\
            srcBytes &   -8.994 $\pm$ 4.744 &   -5.373 $\pm$ 3.870 \\
    \#dstTCPflag:ack &   -8.292 $\pm$ 0.227 &   -2.616 $\pm$ 1.952 \\
       stdev\_dstTTL &   -6.934 $\pm$ 0.231 &   -0.241 $\pm$ 0.014 \\
%   min\_srcPktLength &   -4.519 $\pm$ 0.314 &   -2.891 $\pm$ 0.180 \\
%         min\_srcTTL &   -4.192 $\pm$ 0.646 &   -3.619 $\pm$ 0.432 \\
% stdev\_srcPktLength &   -4.068 $\pm$ 0.342 &   -2.231 $\pm$ 0.439 \\
% stdev\_dstPktLength &    3.466 $\pm$ 0.085 &    3.289 $\pm$ 0.253 \\
%    stdev\_srcPktIAT &    3.102 $\pm$ 0.407 &    4.743 $\pm$ 0.475 \\
%            protocol &   -3.043 $\pm$ 0.028 &   -2.157 $\pm$ 0.012 \\
%    stdev\_dstPktIAT &   -2.842 $\pm$ 0.375 &   -4.545 $\pm$ 0.503 \\
%  mean\_srcPktLength &    2.339 $\pm$ 0.435 &    1.777 $\pm$ 0.261 \\
%         max\_srcTTL &    2.153 $\pm$ 0.820 &    2.448 $\pm$ 0.249 \\
%    \#srcTCPflag:fin &   -2.117 $\pm$ 0.066 &   -1.876 $\pm$ 0.045 \\
%      max\_srcPktIAT &   -2.044 $\pm$ 0.271 &   -3.821 $\pm$ 0.415 \\
%    \#srcTCPflag:syn &    1.738 $\pm$ 0.010 &    1.521 $\pm$ 0.005 \\
%   max\_dstPktLength &   -1.256 $\pm$ 0.066 &   -1.187 $\pm$ 0.137 \\
%  mean\_dstPktLength &    1.200 $\pm$ 0.019 &    1.008 $\pm$ 0.085 \\
%        mean\_srcTTL &   -0.858 $\pm$ 0.533 &   -0.709 $\pm$ 0.417 \\
%    \#dstTCPflag:syn &   -0.778 $\pm$ 0.021 &   -1.020 $\pm$ 0.011 \\
%         max\_dstTTL &   -0.695 $\pm$ 0.028 &   -1.369 $\pm$ 0.052 \\
%             dstPort &   -0.679 $\pm$ 0.002 &   -0.633 $\pm$ 0.004 \\
%      min\_srcPktIAT &   -0.111 $\pm$ 0.977 &   -0.762 $\pm$ 2.837 \\
%   max\_srcPktLength &    0.498 $\pm$ 0.048 &   -0.475 $\pm$ 0.432 \\
%         min\_dstTTL &    0.468 $\pm$ 0.023 &   -0.197 $\pm$ 0.109 \\
%            duration &   -0.415 $\pm$ 0.007 &   -0.386 $\pm$ 0.042 \\
%             srcPort &    0.345 $\pm$ 0.007 &    0.350 $\pm$ 0.005 \\
%   min\_dstPktLength &    0.268 $\pm$ 0.009 &    0.142 $\pm$ 0.021 \\
%      max\_dstPktIAT &    0.225 $\pm$ 0.267 &    2.307 $\pm$ 0.432 \\
%    \#dstTCPflag:fin &   -0.103 $\pm$ 0.024 &   -0.112 $\pm$ 0.017 \\
%        mean\_dstTTL &   -0.069 $\pm$ 0.016 &    1.436 $\pm$ 0.116 \\
%    \#srcTCPflag:cwr &    0.059 $\pm$ 0.034 &    0.052 $\pm$ 0.013 \\
%       stdev\_srcTTL &   -0.051 $\pm$ 0.025 &   -0.058 $\pm$ 0.012 \\
%    \#dstTCPflag:cwr &    0.016 $\pm$ 0.001 &   -0.014 $\pm$ 0.005 \\

@@

\begin{table}
\caption{Detection performance results for models with backdoor.} 
\label{tab:performance_results_bd}
\begin{tabular}{l r r} \toprule
& Random Forest & Deep Learning \\ \midrule
Accuracy	&	0.9986 $\pm$ 0.0004	&	0.9974 $\pm$ 0.0001		\\
Precision	&	0.9981 $\pm$ 0.0005	&	0.9986 $\pm$ 0.0004		\\
Recall	&	0.9964 $\pm$ 0.0009	&	0.9912 $\pm$ 0.0004		\\
F1	&	0.9972 $\pm$ 0.0007	&	0.9949 $\pm$ 0.0002		\\
Youden	&	0.9957 $\pm$ 0.0011	&	0.9907 $\pm$ 0.0003		\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Efficacy of the backdoor.}
\begin{tabular}{l r r} \toprule
 & Random Forest & Deep Learning \\ \midrule
Forward & 1 & 0,9999 $\pm$ 0,0001 \\
Backward & 1 & 0,9999 $\pm$ 0,0000 \\
\bottomrule
\end{tabular}
\end{table}
